Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-10 ms.tex
added ending sentences to section about comparison between different dust emission models

% one or two last sentence(s) saying two-component model still alive, wasn't
% an artifact of FIRAS, and also the predictions from our data release
% are a suitable alternative for estimating CMB foregrounds and can provide
% a handle on foreground systematics when swapped for other

% nevertheless, ...
% in above paragraph, say which single-MBB beta(s) we find to be favored

>>>>

% in above paragraph, say which single-MBB beta(s) we find to be favored

Nevertheless, we have established that the two-component emission model
remains viable in light of the \PLANCK~HFI data, and that the FIR/submm 
dust SED's preference for two MBB components rather than just one is not
simply an idiosyncracy of the FIRAS spectra. We recommend that those interested
in thermal dust foregrounds in the 100-3000 GHz frequency range use our data 
release to predict unpolarized dust emission, at the very least in order to 
help determine the level at which the choice of dust emission model may 
influence their conclusions.
%last sentence needs work
